---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# diffval

<!-- badges: start -->
<!-- badges: end -->

Find, visualize and explore patterns of 'differential taxa' in vegetation data
(namely in a phytosociological table), using the Differential Value (DiffVal).
DiffVal captures the degree of exclusiveness of a taxon to each of the different
clusters of relevés of a sorted phytosociological table. The patterns of
'differential taxa' are searched through mathematical optimization algorithms,
resorting the table while maximizing the sum of the DiffVal for all the taxa in
the table, i.e. maximizing the Total Differential Value (TotDiffVal or TDV).
Ultimately, TDV optimization aims at obtaining classifications of vegetation
data based on 'differential taxa', as in the traditional phytosociological
(or geobotanical) approach. The 'Gurobi' optimizer, as well as the R package
'gurobi', can be installed from <https://www.gurobi.com/products/gurobi-optimizer/>.
The vignette "Gurobi Installation Guide", from package 'prioritizr', is useful
and can be found here: <https://cran.r-project.org/web/packages/prioritizr/vignettes/gurobi_installation.html>.

## Acknowledgments

T.M.H. was funded by the European Social Fund (POCH and NORTE 2020) and
by National Funds (MCTES), through a FCT – Fundação para a Ciência 
a Tecnologia postdoctoral fellowship (SFRH/BPD/115057/2016), as well as
by National Funds, through the same foundation, under the project
UIDB/04033/2020.

## Installation

You can install the package from GitLab.

```{r, eval = FALSE}
devtools::install_git("https://gitlab.com/point-veg/diffval")
```
